Pre-trained encoders for dialogue: The case of laughter

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Transitions.

One important dialogical feature missing from text data is laughter, which is ubiquitous in our everyday interactions.
We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be any an event or an entity in the discourse (and external perceived event as well).
Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.

@@

@@

\paragraph{Dialogue act grouping}
For our corpora we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
This allows the direct comparison between SWDA and AMI-DA.
With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).
% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

@@

@@

Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought. Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix. However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness \citep{ginzburg2015understanding}, in this case, of a question.
Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
\begin{table}
      \small
  \centering
  \begin{tabularx}{\linewidth}{llL}
    \toprule
    Speaker & DA & Utterance \\ \midrule
        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
    B   & sd	&  Um, as far as spare time, they talked about, \\
    B	& \% & I don't, + I think, \\
    B	& qh & who has any spare time \texttt{<laughter>}? \\
    A	& x & \texttt{<laughter>}.\\
             \bottomrule
  \end{tabularx}
  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
  \label{table:example-qh}
\end{table}

@@

%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
%  - cross-domain pre-training

>>>>

One important dialogical feature missing from text data is laughter, which is ubiquitous in our everyday interactions.
We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be any an event or an entity in the discourse (and external perceived event as well).
Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
Laughter can act as a contextual feature for determining the sincerity of an utterance, in order to understand sincerity of an utterance, e.g. to detect sarcasm \citep{tepperman2006yeah}.

@@

\paragraph{} In the next section, we will present the datasets that we will use in our experiments along with their distinctive features.

@@

\paragraph{Dialogue act grouping}
For our corpora we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
This allows the direct comparison between SWDA and AMI-DA.
With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).

% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

\paragraph{}
Let us turn now to describing the neural network architectures that we used.

@@

The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.

@@

Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought. Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix. However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
\begin{table}
      \small
  \centering
  \begin{tabularx}{\linewidth}{llL}
    \toprule
    Speaker & DA & Utterance \\ \midrule
        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
    B   & sd	&  Um, as far as spare time, they talked about, \\
    B	& \% & I don't, + I think, \\
    B	& qh & who has any spare time \texttt{<laughter>}? \\
    A	& x & \texttt{<laughter>}.\\
             \bottomrule
  \end{tabularx}
  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
  \label{table:example-qh}
\end{table}

@@

%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
%  - cross-domain pre-training
\paragraph{}
Having discussed the experimental results, the final section of the paper provides broader explanations of our findings.
